An Axiomatic Basis for Computer Programming: Review

### 2017-02-17 hoare/paper.tex
Finish conclusion for the first version

Also quantifiers cannot be expressed as boolean expression in ordinary
languages, which doesn't support it \cite{meyer:90}.

So defining predicates is weak part of method overall.

@@

This proof technique not only had a great influence on evolution of software
verification, but also alleviate some of the other problems which exist in
computing word.

Strict definition of subroutines' variables before and after execution, helps
understand purpose and accomplishment for potential user.

Lets not forget that Halting problem is undecidable over Turing machines.

With technique which Hoare suggests we can prove total correctness of program.

But after all, we can gain confidence in reliability and correctness of our
software as much as we believe in deductive logic, validity of our
assumptions and reliability of the electronics.

>>>>

Also quantifiers cannot be expressed as boolean expression in ordinary
languages, which doesn't support it \cite{meyer:90}.\\

Another disadvantage of software verification and modeling overall is a cost.
Because it requires much more precision and rigor, they are always going to be
more expensive than traditional approaches to engineering.

@@

Nowadays nobody writes code from scratch. We rely on quality of underlying
layers. But we can't prove correctness for our program, until we prove
correctness for all underlying layers. \\

It could be the case, when we don't want to spent huge amount of time to prove
software, but not in critical industries. The fundamental basis is required in
these areas.

Like with the bricks, we need to construct base for next level of abstraction,
proving that we don't make mistake which could cost lives.
Can be used different techniques of proof. But most important thing is to be
confident in theory and in practice.
\\

This proof technique not only had a great influence on evolution of software
verification, but also alleviate some of the other difficulties which appears in 
computing word.\\

One of them is a documentation of source code.
Strict definition of subroutine's variables before and after execution, helps
potential user understand purpose and how use it.

It might be a better documentation than the description written at four pages.

Because in principle we don't need understand how to work black box inside, if
we sure how we can use it outside.
Understanding will come with time.
\\

Another issue is maintenance existing code base.
First of all, we won't receive messages about errors, will not spent time on
fixing and debugging.

We will spend time on modeling and proofs instead.
\\

Slowly but surely, after all, we will gain confidence in reliability and
correctness of our software as much as we believe in deductive logic, validity
of our assumptions and reliability of the electronics.
